%%% Bibliography (literature used as a source)
%%%
%%% We employ bibTeX to construct the bibliography. It processes
%%% citations in the text (e.g., the \cite{...} macro) and looks up
%%% relevant entries in the bibliography.bib file.
%%%
%%% The \bibliographystyle command selects, which style will be used
%%% for references from the text. The argument in curly brackets is
%%% the name of the corresponding style file (*.bst). Both styles
%%% mentioned in this template are included in LaTeX distributions.

% \bibliographystyle{plainnat}    %% Author (year)
% \bibliographystyle{unsrt}     %% [number]

% \renewcommand{\bibname}{Bibliography}

%%% Generate the bibliography. Beware that if you cited no works,
%%% the empty list will be omitted completely.

% \bibliography{bibliography}

%%% If case you prefer to write the bibliography manually (without bibTeX),
%%% you can use the following. Please follow the ISO 690 standard and
%%% citation conventions of your field of research.

% \begin{thebibliography}{99}
%
% \bibitem{lamport94}
%   {\sc Lamport,} Leslie.
%   \emph{\LaTeX: A Document Preparation System}.
%   2nd edition.
%   Massachusetts: Addison Wesley, 1994.
%   ISBN 0-201-52983-1.
%
% \end{thebibliography}

\begin{thebibliography}{99}
\setlength\itemsep{0pt}

\bibitem{DBLP:journals/tcs/AlbersH12}
S.~Albers and M.~Hellwig.
\newblock Semi-online scheduling revisited.
\newblock {\em Theor. Comput. Sci.}, 443:1--9, 2012.

\bibitem{AsAFPW97}
J.~Aspnes, Y.~Azar, A.~Fiat, S.~Plotkin, and O.~Waarts.
\newblock On-line load balancing with applications to machine scheduling and
  virtual circuit routing.
\newblock {\em J. ACM}, 44:486--504, 1997.

\bibitem{azar98}
Y.~Azar and O.~Regev.
\newblock On-line bin-stretching.
\newblock In {\em Proc. of Randomization and Approximation Techniques in Computer
  Science (RANDOM)}, pages 71--81. Springer, 1998. 

\bibitem{azar01}
Y.~Azar and O.~Regev.
\newblock On-line bin-stretching.
\newblock {\em Theor. Comput. Sci.} 268(1):17--41, 2001. 

\bibitem{BeChKa00}
P.~Berman, M.~Charikar, and M.~Karpinski.
\newblock On-line load balancing for related machines.
\newblock {\em J. Algorithms}, 35:108--121, 2000.

\bibitem{bsvsv14}
M. B\"ohm, J. Sgall, R. van Stee, and P. Vesel\'y. 
\newblock Better algorithms for online bin stretching.
\newblock 
In {\em Proc. of the 12th Workshop on Approximation and Online Algorithms (WAOA 2014)}, Lecture Notes in Comput. Sci. 8952, pages 23-34, Springer, 2015.

\bibitem{coffman13}
E.~Coffman~Jr., J.~Csirik, G.~Galambos, S.~Martello, and D.~Vigo.
\newblock Bin Packing Approximation Algorithms: Survey and Classification,
\newblock In P.~M. Pardalos, D.-Z. Du, and R.~L. Graham, editors, {\em Handbook
of Combinatorial Optimization}, pages 455--531. Springer New York,
2013.

\bibitem{EbJaSg09}
T.~Ebenlendr, W.~Jawor, and J.~Sgall.
\newblock Preemptive online scheduling: {O}ptimal algorithms for all speeds.
\newblock {\em Algorithmica}, 53:504--522, 2009.

\bibitem{gabay2013lbv2}
M.~Gabay, N.~Brauner, V.~Kotov.
\newblock Computing lower bounds for semi-online optimization
problems: Application to the bin stretching problem. 
\newblock HAL preprint hal-00921663, version 2,
2013.

\bibitem{gabay2015lbv3}
M.~Gabay, N.~Brauner, V.~Kotov.
\newblock Improved Lower Bounds for the Online Bin Stretching Problem. 
\newblock HAL preprint hal-00921663, version 3,
2015.

\bibitem{Graham69}
R.~L. Graham.
\newblock Bounds on multiprocessing timing anomalies.
\newblock {\em SIAM J. Appl. Math.}, 17:263--269, 1969.

\bibitem{johnson73}
D.~Johnson.
\newblock {\em Near-optimal Bin Packing Algorithms}.
\newblock Massachusetts Institute of Technology, project MAC. Massachusetts
  Institute of Technology, 1973.

\bibitem{kellerer2013}
H.~Kellerer and V.~Kotov.
\newblock An efficient algorithm for bin stretching.
\newblock {\em Operations Research Letters}, 41(4):343--346, 2013.

\bibitem{KeKoST97}
H.~Kellerer, V.~Kotov, M.~G. Speranza, and Z.~Tuza.
\newblock Semi on-line algorithms for the partition problem.
\newblock {\em Oper. Res. Lett.}, 21:235--242, 1997.

\bibitem{PST04}
K.~Pruhs, J.~Sgall, and E.~Torng.
\newblock Online scheduling.
\newblock In J.~Y.-T. Leung, editor, {\em Handbook of Scheduling:
  {Algorithms}, Models, and Performance Analysis}, chapter~15, pages 15--1 --
  15--41. CRC Press, 2004.

\bibitem{ullman71}
J.~Ullman.
\newblock {The Performance of a Memory Allocation Algorithm}.
\newblock {\em Technical Report 100}, 1971.

\bibitem{bohm16}
M. Böhm.
\newblock Lower Bounds for Online Bin Stretching with Several Bins.
\newblock Student Research Forum Papers and Posters at SOFSEM 2016, CEUR WP Vol-1548,
2016.

\bibitem{bsvsv16}
M. Böhm, J. Sgall, R. van Stee, and P. Veselý. 
\newblock A Two-Phase Algorithm for Bin Stretching with Stretching Factor 1.5.
\newblock ArXiv preprint arXiv:1601.08111v2,
2016.

\bibitem{gabay2013}
M.~Gabay, V.~Kotov, N.~Brauner.
\newblock Semi-online bin stretching with bunch techniques.
\newblock HAL preprint hal-00869858,
2013.

\bibitem{zobrist}
Zobrist, Albert L.
\newblock A new hashing method with application for game playing.
\newblock ICCA journal 13.2: 69-73.
1970.

\bibitem{anst04}
E.~Angelelli, A.~B.~Nagy, M.~G.~Speranza and Z. Tuza.
\newblock The on-line multiprocessor scheduling problem with known sum of the tasks.
\newblock Journal of Scheduling, 7(6), 421-428,
2004.

\end{thebibliography}