\begingroup
\let\clearpage\relax
\let\chapter\paragraph
\renewcommand\bibname{Journal papers}
\begin{thebibliography}{99}
\setlength\itemsep{0pt}

\bibitem{downscaling}
M. Bienkowski, M. Böhm, Ł. Jeż, P. Laskoś-Grabowski, J. Marcinkowski, J. Sgall, A. Spyra, and P. Veselý.
\newblock Logarithmic price of buffer downscaling on line metrics.
\newblock Theoretical Computer Science, 707: 89-93, 2018.

\bibitem{onlinechromatic}
M. Böhm, P. Veselý.
\newblock Online Chromatic Number is PSPACE-Complete.
\newblock Theory Comput. Syst. 62(6): 1366-1391, 2018.

\bibitem{manybins-j}
M. Böhm, J. Sgall, R. van Stee, P. Veselý.
\newblock A two-phase algorithm for bin stretching with stretching factor 1.5.
\newblock J. Comb. Optim. 34(3): 810-828, 2017.

\bibitem{threebins-j}
M. Böhm, J. Sgall, R. van Stee, Pavel Veselý.
\newblock Online bin stretching with three bins.
\newblock J. Scheduling 20(6): 601-621, 2017.

\bibitem{coloredbins}
M. Böhm, G. Dósa, L. Epstein, J. Sgall, and P. Veselý.
\newblock Colored Bin Packing: Online Algorithms and Lower Bounds.
\newblock Algorithmica, Springer, 2016.
\newblock ISSN: 0178-4617.


\end{thebibliography}

\renewcommand\bibname{Papers in conference proceedings}
\begin{thebibliography}{99}
\setlength\itemsep{0pt}

\bibitem{chasing}
N.~Bansal, M. Böhm, M. Eliáš, G. Koumoutsos, and S. W. Umboh.
\newblock Nested Convex Bodies are Chaseable.
\newblock In Proceedings of SODA 2018, pp. 1253-1260, 2018.

\bibitem{jamming}
M. Böhm, Ł Jeż, J. Sgall, and P. Veselý.
\newblock On Packet Scheduling with Adversarial Jamming and Speedup.
\newblock In Proc. of the 15th Workshop on Approximation and Online Algorithms (WAOA 2017), pp. 190-206, 2017.

\bibitem{aggregation}
M. Bienkowski, M. Böhm, J. Byrka, M. Chrobak, C. Dürr, L. Folwarczný, Ł. Jeż, J. Sgall, N. K. Thang, and P. Veselý.
\newblock Online Algorithms for Multi-Level Aggregation.
\newblock In Proceedings of the 24th Annual European Symposium on Algorithms (ESA 2016), Leibniz International Proceedings in Informatics (LIPIcs), pp. 12:1 -- 12:17, 2016.

\bibitem{lookahead-isaac}
M. Böhm, M. Chrobak, Ł. Jeż, F. Li, J. Sgall, and P. Veselý.
\newblock Online Packet Scheduling with Bounded Delay and Lookahead.
\newblock In proceedings of the 27th International Symposium on Algorithms and Computation (ISAAC 2016), 2016.

\bibitem{binstretch-sofsem}
M. Böhm.
\newblock Lower Bounds for Online Bin Stretching with Several Bins.
\newblock In proceedings of SOFSEM 2016 (Student Research Forum Papers / Posters): 1-12, 2016.

\bibitem{onlinecol-iwoca}
M. Böhm, P. Veselý.
\newblock Online Chromatic Number is PSPACE-Complete.
\newblock In Proceedings of IWOCA 2016: 16-28, 2016.

\bibitem{coloredbins-waoa}
M. Böhm, J. Sgall, and P. Veselý.
\newblock Online Colored Bin Packing.
\newblock In Proceedings of WAOA 2014, LNCS, Springer, 2015.

\bibitem{binstretch-waoa}
M. Böhm, J. Sgall, R. van Stee, P. Veselý.
\newblock Better Algorithms for Online Bin Stretching.
\newblock In Proceedings of WAOA 2014: 23-34, 2015.

\end{thebibliography}

\endgroup