%%% The main file. It contains definitions of basic parameters and includes all other parts.

%% Settings for single-side (simplex) printing
% Margins: left 40mm, right 25mm, top and bottom 25mm
% (but beware, LaTeX adds 1in implicitly)
% \documentclass[12pt,a4paper]{report}
% \setlength\textwidth{145mm}
% \setlength\textheight{247mm}
% \setlength\oddsidemargin{15mm}
% \setlength\evensidemargin{15mm}
% \setlength\topmargin{0mm}
% \setlength\headsep{0mm}
% \setlength\headheight{0mm}
% \openright makes the following text appear on a right-hand page
% \let\openright=\clearpage

%% Settings for two-sided (duplex) printing
\documentclass[12pt,a4paper,twoside,openright]{report}
\setlength\textwidth{145mm}
\setlength\textheight{247mm}
\setlength\oddsidemargin{14.2mm}
\setlength\evensidemargin{0mm}
\setlength\topmargin{0mm}
\setlength\headsep{0mm}
\setlength\headheight{0mm}
\let\openright=\cleardoublepage

%% Generate PDF/A-2u
\usepackage[a-2u]{pdfx}
%% Character encoding: usually latin2, cp1250 or utf8:
\usepackage[utf8]{inputenc}

\usepackage[pdfa]{hyperref}

%% Prefer Latin Modern fonts
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{textcomp}

%% Further useful packages (included in most LaTeX distributions)
\usepackage{amsmath}        % extensions for typesetting of math
\usepackage{amsfonts}       % math fonts
\usepackage{amsthm}         % theorems, definitions, etc.
\usepackage{amssymb}
\usepackage{bbding}         % various symbols (squares, asterisks, scissors, ...)
\usepackage{bm}             % boldface symbols (\bm)
\usepackage{graphicx}       % embedding of pictures
\usepackage{fancyvrb}       % improved verbatim environment
% \usepackage{natbib}         % citation style AUTHOR (YEAR), or AUTHOR [NUMBER]
% \usepackage[style=numeric,maxbibnames=99,defernumbers=true,sorting=none,hyperref=true]{biblatex}

\usepackage[nottoc]{tocbibind} % makes sure that bibliography and the lists
			    % of figures/tables are included in the table
			    % of contents
\usepackage{dcolumn}        % improved alignment of table columns
\usepackage{booktabs}       % improved horizontal lines in tables
\usepackage{paralist}       % improved enumerate and itemize
\usepackage[usenames]{xcolor}  % typesetting in color
\usepackage{xspace}

\usepackage[noend]{algpseudocode}
\usepackage{algorithm}
%\usepackage{thmtools, thm-restate}
\algnewcommand{\IIf}[1]{\State\algorithmicif\ #1 \algorithmicthen}
\algnewcommand{\EndIIf}{\unskip\ \algorithmicend\ \algorithmicif}


%%% Basic information on the thesis

% Thesis title in English (exactly as in the formal assignment)
\def\ThesisLargeTitle{Online Bin Stretching:\\ \mbox{Algorithms and Computer Lower Bounds}}
\def\ThesisTitle{Online Bin Stretching: Algorithms and Computer Lower Bounds}

% Author of the thesis
\def\ThesisAuthor{Martin Böhm}

% Year when the thesis is submitted
\def\YearSubmitted{2018}

% Name of the department or institute, where the work was officially assigned
% (according to the Organizational Structure of MFF UK in English,
% or a full name of a department outside MFF)
\def\Department{Computer Science Institute of Charles University}

% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Institute}

% Thesis supervisor: name, surname and titles
\def\Supervisor{prof. RNDr. Jiří Sgall, DrSc.}

% Supervisor's department (again according to Organizational structure of MFF)
\def\SupervisorsDepartment{Computer Science Institute of Charles University}

% Study programme and specialization
\def\StudyProgramme{Computer Science}
\def\StudyBranch{Discrete Models and Algorithms}

% An optional dedication: you can thank whomever you wish (your supervisor,
% consultant, a person who lent the software, etc.)
\def\Dedication{%

The first person to thank must immediately and irrevocably be my PhD
advisor, Jiří Sgall. The academia has certainly many equally gifted
computer scientists, but he has repeatedly shown to me that a
scientist can harbor both great talent and great humanity.
In low and high points of my doctoral studies alike, he has
always supported me with both scientific insight as well as
encouragement. 

A special thanks goes to my colleague and frequent coauthor, Pavel
Veselý. We have a student paper together that I am very fond of. He
has submitted a PhD thesis at the same time as me on online packet
scheduling; I recommend the reader to take a look at that thesis as
well.

I would also like to mention Rob van Stee, a coauthor of our bin
stretching work. His enthusiasm for the project has often boosted my
own, and our email correspondence was a big motivation for making
progress on the lower bound program.

I would like to thank my parents, Michal and Lenka, as well as my
sister Kristýna, for all their support throughout the years; not to
mention for the excellent Sunday lunches at home. The same goes to the
rest of my family: all four of my grandparents, all four of my aunts
and uncles, and all four of my cousins.

I am grateful to all my friends: Petr Onderka, Lukáš Lánský, Lukáš
Mach, David Marek, Jiří Maršík, Josef Kakrda and many more. Special
thanks to Petr and Tereza for proofreading parts of this thesis.

Finally, I would like to thank my life partner Tereza Hulcová for
everything.

}

% Abstract (recommended length around 80-200 words; this is not a copy of your thesis assignment!)
\def\Abstract{%

We investigate a problem in semi-online algorithm design, called
Online Bin Stretching. The problem can be understood as an online
repacking problem: the goal of the algorithm is to repack items of
various sizes into $m$ containers of identical size $R>1$. The input
items arrive one by one and the algorithm must assign an item to a
container before the next item arrives.

A speciality of this problem is that there is a specific guarantee
made to the algorithm: the algorithm learns at the start of the input
that there exists a packing of all input items into $m$ containers of
capacity $1$.

Our goal is to design algorithms for this problem which successfully
pack the entire incoming sequence one by one while requiring the
lowest container capacity $R$ possible.

In this thesis, we show several new results about Online Bin
Stretching: First, we design an algorithm that is able to pack the
entire input into $m$ containers of capacity $1.5$ regardless of what
the vale of $m$ will be. Second, we show a specialized algorithm for
the setting of just $3$ containers; this algorithm is able to pack
into 3 bins of capacity $1.375$. Finally, we design and implement an
involved search algorithm which is able to find lower bounds for
Online Bin Stretching -- and in fact we show the best known lower
bounds for $3 \le m \le 9$.
}

% 3 to 5 keywords (recommended), each enclosed in curly braces
\def\Keywords{%
{bin stretching} {online scheduling} {bin packing} {online algorithms} {computer search} }

%% The hyperref package for clickable links in PDF and also for storing
%% metadata to PDF (including the table of contents).
%% Most settings are pre-set by the pdfx package.
\hypersetup{unicode}
\hypersetup{breaklinks=true}

% Definitions of macros (see description inside)
\include{macros}

% Title page and various mandatory informational pages
\begin{document}
\include{title}

%%% A page with automatically generated table of contents of the doctoral thesis

\tableofcontents

%%% Each chapter is kept in a separate file
\newpage
\input{intro/preface}
\input{intro/model}
\input{intro/binstretch}
\input{intro/history}
\newpage
\input{intro/contributions}

\newpage
\input{manybins/manybins}
\input{manybins/classification}
\input{manybins/firstphase}
\input{manybins/huge}
\input{manybins/regular}
\input{manybins/conclusion}

\newpage
\input{threebins/threebins}
\input{threebins/gs}
\input{threebins/algo}
\input{threebins/analysis}
\input{threebins/largecase}
\input{threebins/standardcase}
\input{threebins/lps}
\input{threebins/formalproofs}

\newpage
\input{lowerbounds/lowerbound}
\input{lowerbounds/minimax}
\input{lowerbounds/game}
\input{lowerbounds/algorithm}
\input{lowerbounds/dynprog}
\input{lowerbounds/caching}
\input{lowerbounds/pruning}
\input{lowerbounds/monotonicity}
\input{lowerbounds/parallel}
\input{lowerbounds/results}
\input{lowerbounds/instance}
\input{lowerbounds/verification}

\newpage
\input{epilogue/epilog}

%%% Bibliography
\include{bibliography}

%%% Figures used in the thesis (consider if this is needed)
% 
\renewcommand*\listfigurename{List of figures}
\listoffigures

%%% Doctoral theses must contain a list of author's publications

\chapwithtoc{List of publications}
\input{publications}

\openright
\end{document}
