\section{Contributions of this thesis}\label{sec:contrib}

% \todo{Expand this section, too.}

\begin{enumerate}
\item We present a new algorithm for \binstretch
with a stretching factor of $1.5$.  We build on the two-phase approach
which appeared previously in~\cite{kellerer2013,gabay2013}. In this
approach, the first phase tries to fill some bins close to $R-1$ and
achieve a fixed ratio between these bins and empty bins, while the
second phase uses the bins in blocks of fixed size and analyzes each
block separately. 

To reach $1.5$, we needed to significantly improve the analysis using
amortization techniques (represented by a weight function in our
presentation) to amortize among blocks and bins of different types.

This section uses results and text from the published paper

\noindent\textit{Böhm, Sgall, van Stee, Veselý: "A two-phase algorithm
for bin stretching with stretching factor 1.5." Journal of
Combinatorial Optimization 34.3 (2017): 810-828.}

\item We present a specialized algorithm for the subproblem where the
number of bins is fixed to be 3. Our algorithm achieves stretching
factor of $11/8 = 1.375$.  This is the first improvement of the
stretching factor $1.4$ of Azar and Regev~\cite{azar98}.

This section uses results and text from the published paper

\noindent\textit{Böhm, Sgall, van Stee, Veselý: "Online bin
stretching with three bins." Journal of Scheduling 20.6 (2017):
601-621.}

\item We present a new lower bound of $45/33 = 1.\overline{36}$ for
\binstretch on three bins, along with a lower bound of $19/14$ on four
and five bins which is the first non-trivial lower bound for four and
five bins. We build on the paper of Gabay et al.~\cite{gabay2013lbv2}
but significantly change the implementation, both technically and
conceptually. The lower bound of $19/14$ for four bins is
independently shown in \cite{gabay2015lbv3}.

This section uses results and text from the conference paper:

\noindent\textit{Böhm: "Lower Bounds for Online Bin Stretching with
Several Bins." SOFSEM (Student Research Forum Papers/Posters) (2016).}

\item We extend the implementation of the lower bound by adding
parallelization, which allows us to go quite a bit beyond our original
lower bounds. In particular, in the setting with three bins, we give a
new lower bound of $112/82 \approx 1.366$. We also extend the lower
bound of $19/14$ to six, seven, eight and nine bins, which strongly
suggests that this might be a good candidate for a general lower
bound.

These results first appear in this thesis.

\end{enumerate}