\section{The sequential algorithm}\label{sec:minimax}

Our implemented algorithm is a parallel, multi computer implementation
of the minimax game search algorithm. We now describe a pseudocode of
its sequential version. The pecularities of our algorithm (caching,
pruning, parallelization) are described in the following sections.

One of the differences between our algorithm and the algorithm of
Gabay et al. \cite{gabay2013lbv2} is that our algorithm makes no use
of alpha-beta pruning -- indeed, as either \algo or \adversary have a
winning strategy from each bin configuration, there is no need to use
this type of pruning.

\begin{algorithm}
\caption{Procedure $\evaladv$}
Input is a bin configuration $C = (\calL, \calI)$.
% \label{alg:bounded}
\begin{algorithmic}[1]
\State \algorithmicif\ the configuration is cached (Section~\ref{sec:4:caching}), \Return the value found in cache.
% \item\label{step:heuristics} Apply \adversary-based heuristics (Section \ref{subsec:heuristics}).
\State Create a list $L$ of items which can be sent as the next step of the player \adversary (Section \ref{subsec:test}).
\For{every item size $i$ in the list $L$}
\State Recurse by running $\evalalg(C,i)$.
\State \algorithmicif\ $\evalalg(C,i)$ returns $0$ (the configuration is winning for player \adversary), stop the cycle and \Return $0$.
\EndFor
% \State \algorithmicelse\ continue with the next item size.
\State \algorithmicif\ the evaluation reaches this step, store the configuration in the cache and \Return $1$ (player \algo wins).

\end{algorithmic}
\end{algorithm}


\begin{algorithm}
\caption{Procedure $\evalalg$}
Input is a bin configuration $C = (\calL,\calI)$ and item $i$.
\begin{algorithmic}[1]
\State Prune the tree using known algorithms (Section \ref{sec:4:gs}).
\For{any one of the $m$ bins}
\If{$i$ can be packed into the bin so that its load is at most $R-1$}
\State Create a configuration $C'$ that corresponds to this packing.
\State Run $\evaladv(C')$.
\State \algorithmicif\ $\evaladv(C')$ returns 1, \Return 1 as well.
\EndIf
\EndFor
\State \algorithmicif\ we reach this step, no placement of $i$ results in victory of \algo; \Return 0.
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Procedure $\Sequential$}
\noindent Input is a bin configuration $C = (\calL,\calI)$. 
\begin{algorithmic}[1]
\State Fix parameters $m,R,S$.
\State Run $\evaladv(C)$.
\If{$\evaladv(C)$ returns $0$}
\State \Return success (a lower bound exists).
\Else
\State \Return failure.
\EndIf
\end{algorithmic}
\end{algorithm}
